{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-09-27 ident_manu.tex
added better tables and figures for initial and structural analyses

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Sep 6 12:52:12 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

~~Chla specific absorption at 490 nm&\textit{astar490}&$7.41\times 10^{-4}$\tabularnewline
~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.91\times 10^{-5}$\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.34\times 10^{-5}$\tabularnewline

@@

~~maximum growth rate&\textit{umax}&$0.06$\tabularnewline

@@

~~phytoplankton growth respiration coefficient&\textit{respg}&$8.28\times 10^{-3}$\tabularnewline
~~N-uptake rate measured at umax&\textit{vmaxN}&$8.15\times 10^{-3}$\tabularnewline
~~phytoplankton basal respiration coefficient&\textit{respb}&$6.93\times 10^{-3}$\tabularnewline
~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.41\times 10^{-3}$\tabularnewline
~~minimum N cell-quota&\textit{QminN}&$4.25\times 10^{-3}$\tabularnewline
~~coefficient for non-limiting nutrient&\textit{aN}&$4.2\times 10^{-3}$\tabularnewline
~~P-uptake rate measured at umax&\textit{vmaxP}&$4.19\times 10^{-3}$\tabularnewline
~~phytoplankton volume/cell&\textit{volcell}&$4.05\times 10^{-3}$\tabularnewline

@@

~~half-saturation constant for N&\textit{Kn}&$3.03\times 10^{-4}$\tabularnewline
~~minimum P cell-quota&\textit{QminP}&$1.4\times 10^{-7}$\tabularnewline

@@

~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.58\times 10^{-3}$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.19\times 10^{-3}$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.89\times 10^{-3}$\tabularnewline
~~zooplankton carbon/individual&\textit{ZQc}&$9.48\times 10^{-5}$\tabularnewline
~~zooplankton phosphorus/individual&\textit{ZQp}&$3.63\times 10^{-5}$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.1\times 10^{-3}$\tabularnewline
~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.59\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.11\times 10^{-3}$\tabularnewline
~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.95\times 10^{-3}$\tabularnewline
~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.68\times 10^{-4}$\tabularnewline
~~maximum rate of nitrification per day&\textit{nitmax}&$4.91\times 10^{-4}$\tabularnewline
~~NH4 rate constant for nitrification&\textit{KNH4}&$4.12\times 10^{-4}$\tabularnewline
~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.93\times 10^{-4}$\tabularnewline

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%

@@

@@

~~\footnotesize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$2$&$7.26$&$5.4$&-&$5.35$&-&$7.72$&$7.91$&-\tabularnewline
~~\footnotesize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.81$\tabularnewline
~~\footnotesize{\textit{astarOMA}}&$3$&-&-&$3.73$&-&-&-&-&$9.65$\tabularnewline
~~\footnotesize{\textit{astarOMZ}}&$3$&$7.5$&$5.51$&-&$6.01$&-&$7.88$&$7.91$&-\tabularnewline

@@

~~\footnotesize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
~~\footnotesize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
~~\footnotesize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$2$&-&-&-&-&-&-&-&$13.44$\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.4$&-\tabularnewline
~~\footnotesize{\textit{KNH4}}&$2$&$4.04$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNO3}}&$2$&-&-&-&-&$9.1$&-&-&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$2$&-&-&$1.06$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG1}}&$3$&$4.1$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$3$&-&-&$6.01$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.78$\tabularnewline
~~\footnotesize{\textit{KO2}}&$3$&-&-&-&-&-&$14.25$&$12.35$&-\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$3$&-&$1.28$&-&$1.99$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KG2}}&$4$&-&-&-&$11.17$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$4$&-&-&$6.08$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.5$\tabularnewline
~~\footnotesize{\textit{KstarO2}}&$4$&$4.29$&-&-&-&-&$14.34$&$13.61$&-\tabularnewline
~~\footnotesize{\textit{KGcdom}}&$5$&$4.41$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KO2}}&$5$&-&-&$8.44$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{nitmax}}&$6$&-&-&$10.12$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNH4}}&$7$&-&-&$10.17$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{KNO3}}&$8$&-&-&$13.94$&-&-&-&-&-\tabularnewline

@@

~~\footnotesize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\footnotesize{\textit{ediblevector(Z1)}}&$2$&$1.13$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{mA}}&$2$&-&-&$1.16$&$1.28$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$2$&-&-&-&-&$3.38$&-&-&-\tabularnewline
~~\footnotesize{\textit{umax}}&$2$&-&$1.09$&-&-&-&$1.18$&$1.18$&-\tabularnewline
~~\footnotesize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$2.75$\tabularnewline
~~\footnotesize{\textit{alpha}}&$3$&-&-&$1.43$&$1.98$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{ediblevector(Z1)}}&$3$&-&$2.14$&-&-&-&$3.22$&$2.87$&-\tabularnewline
~~\footnotesize{\textit{umax}}&$3$&$1.23$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{alpha}}&$4$&$1.64$&$4.3$&-&-&-&-&$7.17$&-\tabularnewline
~~\footnotesize{\textit{ediblevector(Z1)}}&$4$&-&-&$1.83$&$3.15$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$4$&-&-&-&-&-&$5.2$&-&-\tabularnewline
~~\footnotesize{\textit{alpha}}&$5$&-&-&-&-&-&$9.72$&-&-\tabularnewline
~~\footnotesize{\textit{Qc}}&$5$&-&-&$3.18$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{vmaxN}}&$5$&$8$&$14.42$&-&-&-&-&$14.48$&-\tabularnewline
~~\footnotesize{\textit{Athresh}}&$6$&$8.32$&-&-&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{respg}}&$6$&-&$14.56$&$3.65$&-&-&-&-&-\tabularnewline
~~\footnotesize{\textit{vmaxN}}&$7$&-&-&$4$&-&-&-&-&-\tabularnewline

@@

~~\footnotesize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\footnotesize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\footnotesize{\textit{ZKa}}&$2$&-&$3.48$&-&-&-&$5.38$&$4.15$&-\tabularnewline
~~\footnotesize{\textit{ZQn}}&$2$&-&-&$2.38$&$3.84$&$5.97$&-&-&$4.1$\tabularnewline
~~\footnotesize{\textit{Zm}}&$3$&-&-&$2.74$&-&-&-&-&$11.52$\tabularnewline
~~\footnotesize{\textit{Zumax}}&$3$&-&-&-&$5.94$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Zm}}&$4$&-&-&-&$6.9$&-&-&-&-\tabularnewline
~~\footnotesize{\textit{Zumax}}&$4$&-&-&$3.59$&-&-&-&-&-\tabularnewline

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.1$\tabularnewline
~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.27$\tabularnewline
~~3&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$2.37$\tabularnewline
~~4&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.41$\tabularnewline
~~5&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.54$\tabularnewline
~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$4.9$\tabularnewline
~~7&\footnotesize{\textit{Zm}}&$3$\textsuperscript{Z}&$4.92$\tabularnewline
~~8&\footnotesize{\textit{Zumax}}&$4$\textsuperscript{Z}&$4.94$\tabularnewline
~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$5.03$\tabularnewline
~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.98$\tabularnewline
~~4&\footnotesize{\textit{mA}}&$2$\textsuperscript{P}&$8.27$\tabularnewline
~~5&\footnotesize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$10.08$\tabularnewline
~~6&\footnotesize{\textit{alpha}}&$3$\textsuperscript{P}&$10.09$\tabularnewline
~~7&\footnotesize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.83$\tabularnewline
~~1&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$4.79$\tabularnewline
~~3&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$6.88$\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$1.18$\tabularnewline
~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$3.18$\tabularnewline
~~4&\footnotesize{\textit{KG1}}&$1$\textsuperscript{OM}&$7.5$\tabularnewline
~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
~~3&\footnotesize{\textit{umax}}&$2$\textsuperscript{P}&$2.74$\tabularnewline
~~4&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.86$\tabularnewline
~~5&\footnotesize{\textit{ZKa}}&$2$\textsuperscript{Z}&$5.44$\tabularnewline
~~1&\footnotesize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\footnotesize{\textit{umax}}&$1$\textsuperscript{P}&$4.9$\tabularnewline
~~3&\footnotesize{\textit{vmaxP}}&$2$\textsuperscript{P}&$6.84$\tabularnewline
~~4&\footnotesize{\textit{ZQn}}&$2$\textsuperscript{Z}&$14.13$\tabularnewline

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "footnotesize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%

@@

~~1&\footnotesize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\footnotesize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.17$\tabularnewline
~~3&\footnotesize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.88$\tabularnewline

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Fri Sep 23 17:24:42 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

~~Chla specific absorption at 490 nm&\textit{astar490}&$7.51\times 10^{-4}$\tabularnewline
~~OMZ specific absorption at 490 nm&\textit{astarOMZ}&$4.92\times 10^{-5}$\tabularnewline
~~OMA specific absorption at 490 nm&\textit{astarOMA}&$4.39\times 10^{-5}$\tabularnewline

@@

~~maximum growth rate&\textit{umax}&$0.05$\tabularnewline

@@

~~phytoplankton growth respiration coefficient&\textit{respg}&$8.36\times 10^{-3}$\tabularnewline
~~N-uptake rate measured at umax&\textit{vmaxN}&$8.12\times 10^{-3}$\tabularnewline
~~phytoplankton basal respiration coefficient&\textit{respb}&$6.94\times 10^{-3}$\tabularnewline
~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline
~~minimum N cell-quota&\textit{QminN}&$4.32\times 10^{-3}$\tabularnewline
~~P-uptake rate measured at umax&\textit{vmaxP}&$4.27\times 10^{-3}$\tabularnewline
~~coefficient for non-limiting nutrient&\textit{aN}&$4.23\times 10^{-3}$\tabularnewline
~~phytoplankton volume/cell&\textit{volcell}&$4.13\times 10^{-3}$\tabularnewline

@@

~~half-saturation constant for N&\textit{Kn}&$2.77\times 10^{-4}$\tabularnewline
~~minimum P cell-quota&\textit{QminP}&$8.34\times 10^{-8}$\tabularnewline

@@

~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline
~~zooplankton carbon/individual&\textit{ZQc}&$9.38\times 10^{-5}$\tabularnewline
~~zooplankton phosphorus/individual&\textit{ZQp}&$3.69\times 10^{-5}$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline
~~O2 concentration that inhibits denitrification&\textit{KstarO2}&$3.04\times 10^{-3}$\tabularnewline
~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline
~~half-saturation concentration for O2 utilization&\textit{KO2}&$5.85\times 10^{-4}$\tabularnewline
~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline
~~maximum rate of nitrification per day&\textit{nitmax}&$4.99\times 10^{-4}$\tabularnewline
~~NH4 rate constant for nitrification&\textit{KNH4}&$4.17\times 10^{-4}$\tabularnewline

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Parameter",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist1", rowname = parms, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), colheads = colnms, rgroupTexCmd = NULL)%

@@

{\scriptsize

@@

~~\scriptsize{\textit{astar490}}&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$&$1$\tabularnewline
~~\scriptsize{\textit{astarOMA}}&$2$&$7.33$&$5.42$&-&$5.36$&-&$7.78$&$7.87$&-\tabularnewline
~~\scriptsize{\textit{astarOMZ}}&$2$&-&-&$1.39$&-&-&-&-&$4.73$\tabularnewline
~~\scriptsize{\textit{astarOMA}}&$3$&-&-&$3.87$&-&-&-&-&$10.04$\tabularnewline
~~\scriptsize{\textit{astarOMZ}}&$3$&$7.58$&$5.51$&-&$6.02$&-&$7.91$&$7.87$&-\tabularnewline

@@

~~\scriptsize{\textit{KG1}}&$1$&-&-&$1$&-&-&$1$&-&$1$\tabularnewline
~~\scriptsize{\textit{KG2}}&$1$&-&-&-&-&-&-&$1$&-\tabularnewline
~~\scriptsize{\textit{KGcdom}}&$1$&-&$1$&-&$1$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KstarO2}}&$1$&-&-&-&-&$1$&-&-&-\tabularnewline
~~\scriptsize{\textit{nitmax}}&$1$&$1$&-&-&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KG1}}&$2$&-&$1.12$&-&$1.93$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KG2}}&$2$&-&-&$6$&-&-&-&-&$13.43$\tabularnewline
~~\scriptsize{\textit{KGcdom}}&$2$&-&-&-&-&-&$1.47$&$1.39$&-\tabularnewline
~~\scriptsize{\textit{KNH4}}&$2$&$4.03$&-&-&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KG1}}&$3$&$4.09$&-&-&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KG2}}&$3$&-&-&-&$8.19$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KGcdom}}&$3$&-&-&-&-&-&-&-&$13.75$\tabularnewline
~~\scriptsize{\textit{KO2}}&$3$&-&-&-&-&-&$14.07$&$11.96$&-\tabularnewline
~~\scriptsize{\textit{KstarO2}}&$3$&-&-&$6.04$&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KGcdom}}&$4$&$4.19$&-&$6.12$&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{KO2}}&$4$&-&-&-&-&-&-&-&$14.68$\tabularnewline
~~\scriptsize{\textit{KstarO2}}&$4$&-&-&-&$10.65$&-&$14.08$&-&-\tabularnewline
~~\scriptsize{\textit{KO2}}&$5$&$9.47$&-&$8.61$&-&-&-&-&-\tabularnewline

@@

~~\scriptsize{\textit{mA}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\scriptsize{\textit{umax}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\scriptsize{\textit{ediblevector(Z1)}}&$2$&$1.13$&$1.17$&-&-&-&$1.15$&-&-\tabularnewline
~~\scriptsize{\textit{mA}}&$2$&-&-&$1.19$&$1.29$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{Qc}}&$2$&-&-&-&-&$11.57$&-&-&-\tabularnewline
~~\scriptsize{\textit{umax}}&$2$&-&-&-&-&-&-&$1.21$&-\tabularnewline
~~\scriptsize{\textit{vmaxP}}&$2$&-&-&-&-&-&-&-&$7.45$\tabularnewline
~~\scriptsize{\textit{alpha}}&$3$&-&-&$1.44$&$1.98$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{ediblevector(Z1)}}&$3$&-&-&-&-&-&-&$2.9$&-\tabularnewline
~~\scriptsize{\textit{umax}}&$3$&$2.73$&$2.11$&-&-&-&$3.26$&-&-\tabularnewline
~~\scriptsize{\textit{alpha}}&$4$&$3.55$&$4.57$&-&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{ediblevector(Z1)}}&$4$&-&-&$2.09$&$4.09$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{Qc}}&$4$&-&-&-&-&-&$4.98$&-&-\tabularnewline
~~\scriptsize{\textit{vmaxN}}&$4$&-&-&-&-&-&-&$4.9$&-\tabularnewline
~~\scriptsize{\textit{alpha}}&$5$&-&-&-&-&-&$10.11$&-&-\tabularnewline
~~\scriptsize{\textit{Qc}}&$5$&-&-&$2.9$&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{vmaxN}}&$5$&$8.14$&-&-&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{Athresh}}&$6$&$11.27$&-&-&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{respg}}&$6$&-&-&$3.41$&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{vmaxN}}&$7$&-&-&$3.97$&-&-&-&-&-\tabularnewline

@@

~~\scriptsize{\textit{ZKa}}&$1$&-&-&$1$&$1$&$1$&-&-&$1$\tabularnewline
~~\scriptsize{\textit{Zumax}}&$1$&$1$&$1$&-&-&-&$1$&$1$&-\tabularnewline
~~\scriptsize{\textit{ZKa}}&$2$&-&$4.31$&-&-&-&$7.3$&$5.43$&-\tabularnewline
~~\scriptsize{\textit{ZQn}}&$2$&-&-&$3.18$&$6.32$&$9.76$&-&-&$8.54$\tabularnewline
~~\scriptsize{\textit{Zm}}&$3$&-&-&$4.57$&-&-&-&-&-\tabularnewline
~~\scriptsize{\textit{Zumax}}&$3$&-&-&-&$6.93$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{Zm}}&$4$&-&-&-&$11.86$&-&-&-&-\tabularnewline
~~\scriptsize{\textit{Zumax}}&$4$&-&-&$5.2$&-&-&-&-&-\tabularnewline

@@

% second heuristic, all states
%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist2", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%
\begin{table}[!tbp]
{\scriptsize
\caption{Parameter identifiability (as $\gamma$, \cref{gameq}) for relevant state variables.  Selections followed the second heuristic where parameters were selected independent of category from most to least sensitive until $\gamma > 15$.  Rank describes the relative parameter sensitivity in each category for each state variable (O: optics, OM: organic matter, P: phytoplankton, T: temperature, Z: zooplankton). See \cref{fig:heurist_stts} for a graphical illustration.\label{tab:heurist2}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Selections by state variable}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Rank}&\multicolumn{1}{c}{$\gamma$}\tabularnewline
\hline
{Ammonium}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1$\textsuperscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.9$\tabularnewline
\hline
{Chlorophyll}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.18$\tabularnewline
\hline
{Dissolved Oxygen}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$2.17$\tabularnewline
~~3&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$2.31$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$2.37$\tabularnewline
~~5&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$4.69$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$4.91$\tabularnewline
~~7&\scriptsize{\textit{Zm}}&$3$\textsuperscript{Z}&$6.73$\tabularnewline
~~8&\scriptsize{\textit{Zumax}}&$4$\textsuperscript{Z}&$6.81$\tabularnewline
\hline
{Irradiance}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$4.41$\tabularnewline
~~3&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$7.54$\tabularnewline
~~4&\scriptsize{\textit{mA}}&$2$\textsuperscript{P}&$8.17$\tabularnewline
~~5&\scriptsize{\textit{KGcdom}}&$1$\textsuperscript{OM}&$9.44$\tabularnewline
~~6&\scriptsize{\textit{alpha}}&$3$\textsuperscript{P}&$9.66$\tabularnewline
~~7&\scriptsize{\textit{Zumax}}&$3$\textsuperscript{Z}&$10.79$\tabularnewline
\hline
{Nitrate}&&&\tabularnewline
~~1&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$1$\tabularnewline
\hline
{OM1}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$1.15$\tabularnewline
~~3&\scriptsize{\textit{KG1}}&$1$\textsuperscript{OM}&$3.87$\tabularnewline
\hline
{OM2}&&&\tabularnewline
~~1&\scriptsize{\textit{mA}}&$1$\textsuperscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsuperscript{T}&$1.05$\tabularnewline
~~3&\scriptsize{\textit{umax}}&$2$\textsuperscript{P}&$2.46$\tabularnewline
~~4&\scriptsize{\textit{Zumax}}&$1$\textsuperscript{Z}&$2.91$\tabularnewline
\hline
{Phosphate}&&&\tabularnewline
~~1&\scriptsize{\textit{ZKa}}&$1$\textsuperscript{Z}&$1$\tabularnewline
~~2&\scriptsize{\textit{umax}}&$1$\textsuperscript{P}&$11.45$\tabularnewline
~~3&\scriptsize{\textit{vmaxP}}&$2$\textsuperscript{P}&$11.48$\tabularnewline
~~4&\scriptsize{\textit{ZQn}}&$2$\textsuperscript{Z}&$13.74$\tabularnewline
\hline
\end{tabular}\end{center}}

@@

%latex.default(totab[, -c(1, 2)], file = "", rowlabel = "Selections by state variable",     caption = cap_val, caption.loc = "top", size = "scriptsize",     label = "tab:heurist3", rowname = sels, rgroup = unique(stts),     n.rgroup = as.numeric(table(stts)), colheads = colnms, rgroupTexCmd = NULL)%

@@

~~1&\scriptsize{\textit{mA}}&$1$\textsubscript{P}&$1$\tabularnewline
~~2&\scriptsize{\textit{nitmax}}&$1$\textsubscript{OM}&$1.16$\tabularnewline
~~3&\scriptsize{\textit{Zumax}}&$1$\textsubscript{Z}&$2.9$\tabularnewline
~~4&\scriptsize{\textit{Tref(nospA+nospZ)$_{p1}$}}&$1$\textsubscript{T}&$3.46$\tabularnewline
~~5&\scriptsize{\textit{astar490}}&$1$\textsubscript{O}&$4.25$\tabularnewline
